Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-29 W13report.tex
Spell check

As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
on the same normalization.

Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
Using a Monte Carlo approach we 
estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
detections come primarily from detection of the ringing around stars.

>>>>

As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
on the same normalization.

Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
Using a Monte Carlo approach we 
estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
detections come primarily from detection of the ringing around stars.
